Integrated farming and global warming mitigation in Brazil

### 2022-09-20 manuscript/manuscript.qmd
Add schedule, improve diagrams, add text.

library(DiagrammeR)

@@

    1.4 What are the effects of ICLF system over soil properties?

@@

@@

  graph [layout = dot, rankdir = TD, nodesep = 0.9, ranksep = 0.3]

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.5,
        fontsize = 12]

  edge [penwidth = 1.5]

@@

  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]

  edge [penwidth = 1.5]

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.9,
        fontsize = 12]

  a [label = 'Degraded \n Pastures']
  b [label = 'Temperature']
  c [label = 'Precipitation']
  d [label = 'Potential \n Evapotranspiration']
  e [label = 'Soil Texture']
  f [label = 'System \n Management']
  g [label = 'LULC/Management \n Time Series']
  h [label = 'Productivity']
  i [label = 'Litter']
  j [label = 'Decomposition Rates']
  k [label = 'Below Ground Carbon']
  l [label = 'Above Ground Carbon']
  m [label = 'Emissions']
  n [label = 'Carbon Balance']

    node [shape = ellipse,
        fontname = Helvetica,
        style = dashed,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.5,
        fontsize = 12]

  1 [label = 'LULC Model']
  2 [label = 'Soil Carbon Model']
  3 [label = 'Productivity Model']
  4 [label = 'Economic Model']

  a -> 1 f -> 1 1 -> g
  g -> 2 b -> 2 c -> 2 d -> 2 e -> 2 i -> 2 j -> 2 2 -> k h -> 2
  g -> 3 b -> 3 c -> 3 e -> 3 3-> h 3 -> i h -> i 2 -> l i -> l h -> m
  h -> 4
  k -> n l -> n m -> n

@@

  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]

  edge [penwidth = 1.5]

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.9,
        fontsize = 12]

  a [label = 'Degraded \n Pastures']
  b [label = 'System \n Management']
  c [label = 'LULC Scenarios']
  d [label = 'LULC/Management \n Time Series']

    node [shape = ellipse,
        fontname = Helvetica,
        style = dashed,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.5,
        fontsize = 12]

  1 [label = 'LULC Model']

  a -> 1 b -> 1 c -> 1 1 -> d

@@

  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]

  edge [penwidth = 1.5]

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.9,
        fontsize = 12]

  a [label = 'LULC/Management \n Time Series']
  b [label = 'Temperature']
  c [label = 'Precipitation']
  d [label = 'Potential \n Evapotranspiration']
  e [label = 'Soil Texture']
  h [label = 'Productivity']
  i [label = 'Litter']
  j [label = 'Decomposition Rates']

  node [shape = ellipse,
        fontname = Helvetica,
        style = dashed,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.5,
        fontsize = 12]

  1 [label = 'Productivity Model']
  2 [label = 'Soil Carbon Model']
  3 [label = 'Economic Model']

  a -> 1 a -> 2 a -> 3

  b -> 1 c -> 1 d -> 1 e -> 1
  1 -> h 1 -> i

  b -> 2 c -> 2 d -> 2 e -> 2 j -> 2 i -> 2

  h -> 3

@@

>>>>

library(DiagrammeR)
library(lubridate)
library(tidyverse)

@@

    1.4. What are the effects of ICLF system over soil properties?

@@

    3.3. Does focusing on lowering net emissions a distraction from lowering gross emissions?

@@

  graph [layout = dot, 
         rankdir = TD, 
         nodesep = 2, 
         ranksep = 0.5,
         tooltip = ' ']

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 2.5,
        width = 3,
        height = 1.2,
        fontsize = 25,
        tooltip = ' ']

  edge [penwidth = 2.5, 
        arrowsize = 2,
        tooltip = ' ']

@@

  graph [layout = dot,
         rankdir = TD, 
         nodesep = 2, 
         ranksep = 0.4,
         tooltip = ' ']

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 2.5,
        width = 3,
        height = 1.2,
        fontsize = 25,
        tooltip = ' ']

  edge [penwidth = 2.5, 
        arrowsize = 2,
        tooltip = ' ']

  a [label = 'Region']
  b [label = 'Species']
  c [label = 'Population']
  d [label = 'Cycle Length']
  e [label = 'Management \n Practices']

  a -> b b -> c
  b -> d b -> e

@@

  graph [layout = dot,
         rankdir = LR, 
         nodesep = 1.2, 
         ranksep = 0.5,
         tooltip = ' ']

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 2.5,
        width = 3,
        height = 1.2,
        fontsize = 25,
        tooltip = ' ']

  edge [penwidth = 2.5, 
        arrowsize = 2,
        tooltip = ' ']

  a [label = 'Pasture']
  b [label = 'Transition \n (ICL)']
  c [label = 'ICLF']

    node [shape = oval,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 2.5,
        width = 3,
        height = 1.2,
        fontsize = 25,
        tooltip = ' ']

  e [label = 'Random Variables']
  f [label = 'Expansion \n Scenario']

      node [shape = diamond,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 2.5,
        width = 3,
        height = 1.2,
        fontsize = 25,
        tooltip = ' ']

  d [label = 'Random \n Selection']

  a -> d b -> c c -> b 
  d -> b e -> b e -> c
  f -> d

@@

grViz(height = 500,
  "digraph {

  graph [layout = dot,
         rankdir = TD, 
         nodesep = 1.2, 
         ranksep = 0.5,
         tooltip = ' ']

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 2.5,
        width = 3,
        height = 1.2,
        fontsize = 25,
        tooltip = ' ']

  edge [penwidth = 2.5, 
        arrowsize = 2,
        tooltip = ' ']

  a [label = 'Biomass']
  b [label = 'Soil Carbon \n (Century)']
  c [label = 'Productivity']
  d [label = 'Revenue']

    node [shape = oval,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 2.5,
        width = 3,
        height = 1.2,
        fontsize = 25,
        tooltip = ' ']

  e [label = 'Population']      
  f [label = 'Climate']
  g [label = 'Species']
  h [label = 'Management \n Practices']

  a -> b a -> c c -> d

  e -> a e -> c
  f -> a f -> b f -> c
  g -> a g ->b g -> c
  h -> d

@@

# Schedule

schedule_table <- 
  bind_rows(
    list(
      activity = "Systematic Review",
      start = "01-10-2022",
      end = "01-06-2023",
      section = 1
    ),
    list(
      activity = "Experts Survey Development",
      start = "01-10-2022",
      end = "01-04-2023",
      section = 1
    ),
    list(
      activity = "Experts Survey Application",
      start = "01-04-2023",
      end = "01-08-2023",
      section = 1
    ),
    list(
      activity = "Model Prototype Development",
      start = "01-10-2022",
      end = "01-09-2023",
      section = 2
    ),
    list(
      activity = "Projection Scenarios Development",
      start = "01-07-2023",
      end = "01-09-2023",
      section = 2
    ),
    list(
      activity = "LULC Projections",
      start = "01-09-2023",
      end = "01-11-2023",
      section = 2
    ),
    list(
      activity = "Benefits Estimations",
      start = "01-11-2023",
      end = "01-04-2024",
      section = 2
    ),
    list(
      activity = "Targeted Review",
      start = "01-01-2024",
      end = "01-06-2024",
      section = 3
    ),
    list(
      activity = "Narrative Discussion",
      start = "01-04-2024",
      end = "01-08-2024",
      section = 3
    ),
    list(
      activity = "Final Manuscript Development",
      start = "01-08-2024",
      end = "01-02-2025",
      section = NA
    )
  )

schedule_table <- schedule_table %>%
  mutate(
    start = dmy(start),end = dmy(end),
    activity = factor(activity, levels = activity)
  ) %>%
  pivot_longer(
    cols = c(start, end),
    names_to = "when",
    values_to = "date"
  )

schedule_table %>%
    ggplot() +
    geom_line(
      aes(x = date, y = activity), 
      size = 3, 
      lineend = "round"
    ) +
    scale_y_discrete(limits = rev) +
    scale_x_date(
      date_labels = "%b-%Y", 
      date_breaks = "6 months", 
      date_minor_breaks = "1 month",
      limits = c(ymd("2022-09-01"), ymd("2025-03-01"))
    ) +
    labs(color = "Section") +
    theme_minimal() + 
    theme(
      text = element_text(family = "sans", size = 15),
      panel.grid.major = element_line(color = "#a9a9a9"),
      axis.title = element_blank(),
      axis.text.x = element_text(angle = 35, vjust = 0.6),
      plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"),
      legend.position = "bottom"
    )
